A Survey on Ordered Binary Decision Diagrams

### 2015-09-12 paper.tex
Add hash-based chaches to hash tables

\paragraph*{Hash Table}
\mbox{} % workaround to get line break after paragraph

Hash tables maintain \textit{key}-\textit{value}-pairs, returning the associated
value for a given key in (amortized) constant time~\cite{BRACE90}.

@@

Moreover, hash tables are useful to generate a reduced graph directly from some
operations by maintaing a hash table associating triples
($var(n)$, $lo(n)$, $hi(n)$) with a single nonterminal node $n$. This is done for
each nonterminal node $n$ generated while executing the
operation~\cite{BRYANT92}.
\tbr

>>>>

\paragraph*{Hash Tables}
\mbox{} % workaround to get line break after paragraph

Hash tables maintain \textit{key}-\textit{value}-pairs, returning the associated
value for a given key in (amortized) constant time. Collisions, i.e. equivalent
value for different keys, are resolved by chaining all associated values in a 
linked list~\cite{BRACE90}.

@@

Moreover, hash tables are useful to generate a reduced graph directly from some
operations by maintaing a hash table associating triples
($var(n)$, $lo(n)$, $hi(n)$) with a single nonterminal node $n$. This is done for
each nonterminal node $n$ generated while executing the
operation~\cite{BRYANT92}.

There exists a special version of hash tables, so-called
\textit{hash-based caches}, which do not resolve collisions, i.e. overwrite
existing entries. \textit{Hash-based caches} issue a cache miss if a looked up
element is not found. \tbr
